Search-Based Test Data Generation for JavaScript Functions with DOM

### 2017-11-05 doc/icse2018/icse2018.tex
Added new version of the papper.

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate}
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{algorithmic}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

\newcommand{\Server}{\emph{Server}\xspace}
\newcommand{\Client}{\emph{Client}\xspace}
\newcommand{\User}{\emph{User}\xspace}
\newcommand{\Validator}{\emph{Validator}\xspace}

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Search-Based Test Data Generation for JavaScript Functions on DOM}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{1}

\author{
  \alignauthor Alexander Elyasov, Wishnu Prasetya, Jurriaan Hage\\ 
  \affaddr{Utrecht University, The Netherlands}\\
  \email{\{a.elyasov,s.w.b.prasetya,j.hage\}@uu.nl}
}

\maketitle
\begin{abstract}

\end{abstract}

@@

\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{ACM proceedings; \LaTeX; text tagging}

@@

Success of any search-based algorithm heavily depends on the choice of the fitness function (FF) that guides the search process. In our case FF is defined on CFG of the program.

\[
\mathcal{F}(n) = 
\]

\[
\mathcal{F}^*(n) = \mathcal{F}(n) + \lambda * \mathcal{F}(n_e)
\]

@@

@@

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%

%\balancecolumns

>>>>

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{longtable}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

\newcommand{\Server}{\emph{Server}\xspace}
\newcommand{\Client}{\emph{Client}\xspace}
\newcommand{\User}{\emph{User}\xspace}
\newcommand{\Validator}{\emph{Validator}\xspace}
\newcommand{\thenBr}{\text{then}}
\newcommand{\elseBr}{\text{else}}
\newcommand{\inFor}{\text{inFor}}
\newcommand{\inWhile}{\text{inWhile}}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
  Paso, Texas USA} 
\acmYear{1997}
\copyrightyear{2016}

\acmPrice{15.00}

\begin{document}
\title{Search-Based Test Data Generation for JavaScript Functions with DOM}

%% \author{
%%   \alignauthor Alexander Elyasov, Wishnu Prasetya, Jurriaan Hage\\ 
%%   \affaddr{Utrecht University, The Netherlands}\\
%%   \email{\{a.elyasov,s.w.b.prasetya,j.hage\}@uu.nl}
%% }

\author{Alexander Elyasov}
\affiliation{%
  \institution{Utrecht University}
  \city{Utrecht} 
  \country{The Netherlands} 
}
\email{a.elyasov@uu.nl}

\author{Wishnu Prasetya}
\affiliation{%
  \institution{Utrecht University}
  \city{Utrecht} 
  \country{The Netherlands} 
}
\email{s.w.b.prasetya@uu.nl}

\author{Jurriaan Hage}
\affiliation{%
  \institution{Utrecht University}
  \city{Utrecht} 
  \country{The Netherlands} 
}
\email{j.hage@uu.nl}

\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings.\footnote{This is an abstract footnote}
\end{abstract}

@@

\keywords{ACM proceedings, \LaTeX, text tagging}

\maketitle

@@

Success of any search-based algorithm heavily relies on the choice of the fitness function (FF) that guides the evolution process. Our search target is a specific branch of the program under test that we want to cover by generating a valid input data. The input is \emph{valid} only if the program normally terminates on it, i.e. without premature exception. Thus, our search target is an ordered pair of CFG nodes $(n_b, n_x)$ where $n_b$ is the label of the target branch, and $n_x$ is the normal exit node of the program. FF for a CFG node is traditionally defined as a combination of the \emph{approach level} and the normalized \emph{branch distance}\cite{arcuri2010does}. 
\[
\mathcal{F}(n) = \text{Approach Level} + \alpha({\text{Branch Distance}})
\]

Therefore, the resulted FF ($\mathcal{F}^*$) is an ordered pair of the FFs of the respective nodes.

\[
\mathcal{F}^*(n_b, n_x) = (\mathcal{F}(n_b), \mathcal{F}(n_x))
\]

@@

To report on cyclomatic complexity we use \emph{jshint}\footnote{http://jshint.com/} (we can also use this tool\footnote{http://jsmeter.info/})

\begin{table*}
  \caption{Summary of the case studies}
  \label{tbl.case.studies}
  %\resizebox{\textwidth}{!}{
    \footnotesize
  \begin{tabular}{l|l|l|r|r|r|c|c|c|c}
    \toprule
    \textbf{case-study} & \textbf{function} & \textbf{type} & \textbf{\#BR} & \textbf{\#LOC} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
    \midrule
    sudoku     & helpMe & (dom,int,int) & & & & + & + & + & - \\
    sudoku     & isGameFinished & (dom) & & & & + & + & + & + \\
    sudoku     & newGame & (dom)        & & & & + & + & + & + \\
    sudoku     & revealAll & (dom)      & & & & + & + & + & - \\
    sudoku     & shuffleBoard & (dom)   & & & & + & - & + & - \\
    \midrule
    phormer    & toggleInfo & (dom,string) & & & & + & + & - & - \\
    \midrule
    hotel RS   & isValidCard & ([int]) & & & & - & - & - & - \\
    hotel RS   & isValidMasterCard & ([int])  & & & & - & - & - & - \\
    \midrule
    apophis    & initShields & (dom,[int],int,int) & & & & + & + & - & -\\
    \midrule
    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & & & & + & + & - & - \\
    bingbong   & initBricks & (dom,[int],int,int) & & & & + & + & - & - \\
    \midrule
    burncanvas & do\_draw & (int,int,int,int,int,int,int) & & & & - & - & - & - \\
    \midrule
    mathjs     & probability\_gamma & (float) & & & & - & - & - & - \\
    \bottomrule
  \end{tabular}
%}
\end{table*}

\begin{table*}
  \caption{Statistics for genetic and random algorithms}
  \label{tbl.stats}
  \resizebox{\textwidth}{!}{
    \footnotesize
    \begin{tabular}{l|rrrr|rrrr|rrrr|rrrr|r|r|r|r|r|r}
      \toprule
      \textbf{name}     & $\bar{x}_R$ & $\bar{x}_G$ & $\bar{x}_{G5}$ & $\bar{x}_{G10}$ & $m_R$ & $m_G$ & $m_{G5}$ & $m_{G10}$ & $\min_R$ & $\min_G$ & $\min_{G5}$ & $\min_{G10}$ & $\max_R$ & $\max_G$ & $\max_{G5}$ & $\max_{G10}$ & \textbf{R-G} & \textbf{R-G5} & \textbf{R-G10} & \textbf{G-G5} & \textbf{G-G10} & \textbf{G5-G10}\\
      \toprule
      helpMe          &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
    $(3,4,\inFor)$    & 3.94        & 7.94        & 10.22          & 11.7          & 3     & 3.5   & 7       & 7       & 1        & 1        & 1          & 1           & 16       & 31      & 63         & 124 & & & & & & \\
    $(5,6,\thenBr)$   & 3.7         & 13.08       & 9.2            & 9.6           & 3     & 7     & 5       & 5.5     & 1        & 1        & 1          & 1           & 14       & 95      & 44         & 105 & & & & & & \\
    $(5,15,\elseBr)$  & 118.64      & 30.14       & 34.12          & 31.68         & 119.5 & 23    & 28.5    & 22      & 4        & 4        & 3          & 1           & 199      & 97      & 167        & 114 & & & & & & \\
    $(9,10,\thenBr)$  & 105.12      & 17.82       & 21.98          & 21.8          & 83.5  & 17    & 17.5    & 18      & 18       & 1        & 2          & 6           & 199      & 53      & 78         & 77  & & & & & & \\
    $(9,14,\elseBr$   & 4.28        & 5.06        & 8.14           & 9.56          & 2.5   & 5     & 4       & 4       & 1        & 1        & 1          & 1           & 17       & 20      & 49         & 74  & & & & & & \\
    \midrule
    isGameFinished    &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
    %% $(5,6,\inFor)$    & 0.02        & 0.1         & 0.12           & 0.1           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 2       & 2          & 2   \\
    $(7,8,\thenBr)$   & 75.18       & 40.54       & 18.86          & 14.66         & 35.5  & 7     & 8       & 11      & 0        & 0        & 0          & 0           & 199      & 199     & 199        & 82  & & & & & & \\
    %% $(7,15,\elseBr)$  & 0           & 0.06        & 0.04           & 0.08          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 0        & 2       & 1          & 2   \\
    $(10,11,\thenBr)$ & 199         & 35.74       & 21.56          & 24.36         & 199   & 10    & 10      & 9       & 199      & 1        & 1          & 1           & 199      & 199     & 199        & 199 & & & & & & \\
    $(10,14,\elseBr)$ & 69.62       & 56.32       & 28.74          & 31.92         & 23.5  & 10    & 16.5    & 18      & 1        & 0        & 0          & 0           & 199      & 199     & 199        & 199 & & & & & & \\
    \midrule
    newGame           &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
    %% $(4,5,\inFor)$    & 0.04        & 0.12        & 0.1            & 0             & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 2       & 1          & 0 \\
    $(6,7,\thenBr)$   & 21.54       & 10.48       & 9.92           & 8.34          & 15    & 7.5   & 7.5     & 7       & 0        & 0        & 0          & 0           & 97       & 53      & 30         & 35 & & & & & & \\
    %% $(6,12,\elseBr)$  & 0.06        & 0.14        & 0.1            & 0.04          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 3       & 2          & 1\\
    \midrule
    revealAll         &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
    $(2,3,\inFor)$    & 31.78       & 24.84       & 34.94          & 28.04         & 24    & 23    & 29      & 22.5    & 4        & 7        & 7          & 10          & 106      & 57      & 129        & 75 & & & & & & \\
    $(4,5,\inFor)$    & 46.12       & 26.22       & 30.1           & 27.64         & 34    & 19    & 26.5    & 22      & 5        & 9        & 9          & 6           & 199      & 78      & 71         & 90 & & & & & & \\
    \midrule
    shuffleBoard      &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & &\\
    %% $(5,6,\inWhile)$  & 0.36        & 0.32        & 0.24           & 0.48          & 0     & 0     & 0.24    & 0       & 0        & 0        & 0          & 0           & 4        & 3       & 2          & 0\\
    $(13,14,\thenBr)$ & 6.38        & 7.7         & 8.72           & 7.86          & 4     & 4     & 8.72    & 4       & 0        & 0        & 0          & 0           & 22       & 67      & 64         & 38 & & & & & & \\
    $(17,18,\thenBr)$ & 5.66        & 11.86       & 16.96          & 17.72         & 3.5   & 5.5   & 16.96   & 3.5     & 0        & 0        & 0          & 0           & 33       & 133     & 86         & 118 & & & & & & \\
    %% $(21,22,\inFor)$  & 199         & 199         & 199            & 199           & 199   & 199   & 199     & 199     & 0        & 0        & 0          & 0           & 199      & 199     & 199        & 199\\
    \midrule
    \midrule
    toggleInfo        &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
    $(2,3,\thenBr)$   & 1.58        & 1.12        & 1.1            & 1             & 1     & 1     & 1       & 1       & 0        & 0        & 0          & 0           & 11       & 4       & 3          & 3 & & & & & & \\
    $(6,7,\thenBr)$   & 1.48        & 9.9         & 17             & 15.3          & 1     & 2     & 4       & 4       & 0        & 0        & 0          & 0           & 8        & 125     & 143        & 136 & & & & & & \\
    \midrule
    \midrule
    isValidCard       &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\ 
    $(3,6,\elseBr)$   & 199         & 2.98        & 3              & 2.82          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 5       & 5          & 4 & & & & & & \\
    $(7,8,\inFor)$    & 199         & 2.92        & 3.04           & 2.96          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 5       & 4          & 5 & & & & & & \\
    $(10,11,\thenBr)$ & 199         & 3           & 2.86           & 3.06          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
    $(10,13,\elseBr)$ & 199         & 2.84        & 2.98           & 3.04          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
    $(14,15,\inFor)$  & 199         & 3.02        & 2.92           & 2.94          & 199   & 3     & 3       & 3       & 199      & 2        & 2          & 2           & 199      & 4       & 5          & 5 & & & & & & \\
    \midrule
    isValidMasterCard & \multicolumn{16}{l}{} \\ 
    $(2,3,\thenBr)$   & 199         & 11.04       & 12.08          & 11.42         & 199   & 10    & 12      & 12      & 199      & 4        & 5          & 5           & 199      & 27      & 32         & 23 & & & & & & \\
    %% isValidVISA       &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
    %% $(2,3,\thenBr)$   & 199         & 6.54        & 6.38           & 6.48          & 199   & 6     & 6       & 6       & 199      & 4        & 3          & 4           & 199      &  14     & 16         & 18  \\
    \midrule
    \midrule
    initShields       &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & &\\
    $(2,3,\inFor)$    & 5           & 5.32        & 5.28           & 5.26          & 5     & 5     & 5       & 5       & 5        & 5        & 5          & 5           & 5        & 6       & 7          & 7 & & & & & & \\
    \midrule
    \midrule
    brickJiggler      &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & &\\
    $(2,3,\thenBr)$   & 5.22        & 5.34        & 5.68           & 5.3           & 5     & 4     & 4       & 4       & 1        & 2        & 1          & 1           & 18       & 39      & 20         & 20 & & & & & & \\
    doPaddlePower     &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
    %% $(5,8,\elseBr)$   & 0.14        & 0.4         & 0.14           & 0.28          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 5       & 3          & 5 \\
    $(10,11,\thenBr)$ & 17.96       & 193.14      & 47.18          & 42.5          & 14.5  & 199   & 17      & 21      & 0        & 3        & 0          & 0           & 53       & 199     & 199        & 199 & & & & & & \\
    %% drawLevel         &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & \\
    %% $(5,6,\thenBr)$   & 0.18        & 0.16        & 0.14           & 0.2           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 2        & 3       & 5          & 5 \\
    %% $(8,9,\inFor)$    & 0.1         & 0.16        & 0.34           & 0.3           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 3        & 5       & 5          & 5 \\
    %% $(10,11,\thenBr)$ & 0.64        & 1.26        & 0.98           & 0.8           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 3        & 7       & 7          & 8 \\
    %% $(10,13,\elseBr)$ & 0.06        & 0.22        & 0.3            & 0.2           & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 3       & 7          & 3 \\
    %% $(14,15,\inFor)$  & 0.08        & 0.34        & 0.3            & 0.36          & 0     & 0     & 0       & 0       & 0        & 0        & 0          & 0           & 1        & 7       & 4          & 6 \\
    \midrule
    initBricks        &             &             &                &               &       &       &         &         &          &          &            &             &          &         &            & & & & & & & \\
    $(6,7,\thenBr)$   & 1.5         & 3           & 2.6            & 2.74          & 1     & 4     & 2       & 2       & 1        & 1        & 1          & 1           & 5        & 5       & 5          & 5 & & & & & & \\
    $(6,10,\elseBr)$  & 29.82       & 5.98        & 5.28           & 7.1           & 13.5  & 5     & 5       & 5       & 1        & 1        & 1          & 1           & 199      & 14      & 13         & 24 & & & & & & \\
    $(11,12,\thenBr)$ & 162.28      & 18.36       & 27.58          & 25.26         & 199   & 13    & 16.5    & 16      & 2        & 5        & 4          & 4           & 199      & 56      & 71         & 77 & & & & & & \\
    $(11,15,\elseBr)$ & 32.44       & 5.9         & 6.02           & 8.1           & 17    & 5     & 6       & 5       & 1        & 1        & 1          & 1           & 199      & 16      & 28         & 55 & & & & & & \\
    $(16,17,\thenBr)$ & 164.06      & 25.14       & 37.48          & 28.64         & 199   & 16    & 12.5    & 16      & 4        & 4        & 1          & 2           & 199      & 199     & 199        & 112 & & & & & & \\
    $(16,20,\elseBr)$ & 57.22       & 8.32        & 12.2           & 10.92         & 23.5  & 6     & 5       & 7       & 1        & 1        & 1          & 1           & 199      & 62      & 68         & 86 & & & & & & \\
    $(21,22,\thenBr)$ & 152.56      & 19.38       & 30.92          & 40.12         & 199   & 13    & 12.5    & 16      & 1        & 1        & 2          & 2           & 199      & 199     & 117        & 149 & & & & & & \\
    $(21,25,\elseBr)$ & 56.34       & 6.88        & 11.56          & 12.82         & 24.5  & 6     & 6       & 6.5     & 2        & 2        & 1          & 1           & 199      & 22      & 91         & 80 & & & & & & \\
    $(29,30,\thenBr)$ & 147.66      & 102.66      & 91             & 96.48         & 199   & 65    & 69.5    & 73      & 2        & 5        & 5          & 5           & 199      & 199     & 199        & 199& & & & & & \\
    $(29,37,\elseBr)$ & 1.46        & 2.5         & 2.52           & 2.78          & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 5        & 6       & 5          & 5 & & & & & & \\
    $(38,39,\thenBr)$ & 145.72      & 108.1       & 94.46          & 89.2          & 184   & 84    & 74.5    & 46.5    & 16       & 4        & 11         & 4           & 199      & 199     & 199        & 199& & & & & & \\
    $(38,46,\elseBr)$ & 1.42        & 2.5         & 2.7            & 2.5           & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 3        & 6       & 6          & 5 & & & & & & \\
    $(47,48,\thenBr)$ & 141.5       & 121         & 112.16         & 108.1         & 185.5 & 199   & 118     & 125.5   & 2        & 5        & 5          & 6           & 199      & 199     & 199        & 199 & & & & & & \\
    $(47,55,\elseBr)$ & 1.54        & 2.44        & 2.5            & 2.46          & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 4        & 5       & 5          & 5 & & & & & & \\
    $(56,57,\thenBr)$ & 111.98      & 96.62       & 94.8           & 90.16         & 108   & 48.5  & 113     & 48      & 3        & 5        & 5          & 4           & 199      & 199     & 199        & 199 & & & & & & \\
    $(56,64,\elseBr)$ & 1.52        & 2.66        & 2.96           & 2.48          & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 3        & 5       & 13         & 5 & & & & & & \\
    $(69,70,\thenBr)$ & 1.42        & 2.64        & 2.8            & 2.52          & 1     & 2     & 2       & 2       & 1        & 1        & 1          & 1           & 3        & 6       & 7          & 6 & & & & & & \\
    $(69,71,\elseBr)$ & 74.98       & 102.98      & 54.82          & 55.42         & 39.5  & 93.5  & 20      & 26      & 1        & 2        & 1          & 1           & 199      & 199     & 199        & 199 & & & & & & \\
    \midrule
    \midrule
    do\_draw           &             &            &               &                &       &       &         &         &           &          &           &             &          &          &           & & & & & & & \\
    $(6,7,\thenBr)$    & 8.88        & 6.67       & 6.4           & 5.84           & 6.5   & 7     & 7       & 6       & 0         & 0        & 0         & 0           & 43       & 13       & 16        & 14 & & & & & & \\
    $(6,12,\elseBr)$   & 12.58       & 5.56       & 5.88          & 5.62           & 9     & 5     & 6       & 6       & 0         & 0        & 0         & 0           & 53       & 17       & 14        & 15 & & & & & & \\
    $(8,11,\elseBr)$   & 131.86      & 18.78      & 24.16         & 19.34          & 143   & 15.5  & 22      & 18      & 6         & 4        & 6         & 5           & 199      & 65       & 53        & 46 & & & & & &\\
    %% $(24,27,\elseBr)$  & 0.02        & 0.08       & 0.18          & 0.06           & 0     & 0     & 0       & 0       & 0         & 0        & 0         & 0           & 1        & 3        & 5         & 3\\
    %% $(36,39,\elseBr)$  & 0.32        & 0.7        & 0.52          & 0.12           & 0     & 0     & 0       & 0       & 0         & 0        & 0         & 0           & 4        & 7        & 7         & 2\\
    %% $(40,43,\elseBr)$  & 0.1         & 0.1        & 0.52          & 0.34           & 0     & 0     & 0       & 0       & 0         & 0        & 0         & 0           & 1        & 2        & 6         & 12\\
    $(44,45,\thenBr)$  & 76.1        & 149.16     & 32.14         & 42.8           & 56    & 199   & 26.5    & 38.5    & 3         & 3        & 0         & 1           & 199      & 199      & 199       & 199 & & & & & & \\
    $(48,49,\thenBr)$  & 36.6        & 114.42     & 29.42         & 31.32          & 25    & 135.5 & 27.5    & 33      & 0         & 0        & 0         & 0           & 185      & 199      & 124       & 41 & & & & & & \\
    \midrule
    \midrule
    probability\_gamma &             &            &               &                &       &       &         &         &           &          &           &             &          &          &           &  & & & & & & \\
    $(4,5,\thenBr)$    & 195.58      & 1.02       & 1             & 1.06           & 199   & 1     & 1       & 1.06    & 28        & 1        & 1         & 1           & 199      & 2        & 1         & 2 & & & & & & \\
    $(6,7,\thenBr)$    & 195.2       & 1.14       & 1.29          & 1.28           & 199   & 1     & 1       & 1.28    & 21        & 1        & 1         & 1           & 199      & 3        & 3         & 4 & & & & & & \\
    $(6,9,\elseBr)$    & 199         & 1.42       & 1.39          & 1.46           & 199   & 1     & 1       & 1.46    & 199       & 1        & 1         & 1           & 199      & 4        & 4         & 4 & & & & & & \\
    $(10,11,\thenBr)$  & 199         & 60.92      & 61.51         & 60.22          & 199   & 61    & 61      & 60.22   & 199       & 45       & 50        & 48          & 199      & 72       & 76        & 76 & & & & & & \\
    $(10,13,\elseBr)$  & 199         & 1.24       & 1.19          & 1.22           & 199   & 1     & 1       & 1.22    & 199       & 1        & 1         & 1           & 199      & 2        & 3         & 3 & & & & & & \\
    $(16,17,\inWhile)$ & 199         & 1.46       & 1.7           & 1.76           & 199   & 1     & 1       & 1.76    & 199       & 1        & 1         & 1           & 199      & 3        & 6         & 8 & & & & & & \\
    $(20,21,\thenBr)$  & 199         & 5.38       & 4.85          & 6.32           & 199   & 5     & 4       & 6.32    & 199       & 1        & 1         & 1           & 199      & 14       & 14        & 25 & & & & & & \\
    $(20,23,\elseBr)$  & 199         & 1.54       & 1.37          & 1.28           & 199   & 1     & 1       & 1.28    & 199       & 1        & 1         & 1           & 199      & 4        & 4         & 3 & & & & & & \\
    $(30,31,\thenBr)$  & 199         & 51.44      &               & 51.96          & 199   & 52    &         & 51.96   & 199       & 42       &           & 42          & 199      & 62       &           & 62 & & & & & & \\
    $(34,35,\thenBr)$  & 199         & 22.66      &               & 23.32          & 199   & 23    &         & 23.32   & 199       & 13       &           & 16          & 199      & 29       &           & 28 & & & & & & \\
    \bottomrule
    \end{tabular}
}
\end{table*}

@@

\cite{wegener2001evolutionary} evolutionary test generation for structural coverage.

\cite{tonella2004evolutionary} evolutionary testing of classes

\cite{wappler2005using} evolutionary testing of object-oriented software.

\cite{wappler2006evolutionary} uses strongly-typed genetic programming and deals with the runtime exceptions.

\cite{lakhotia2007multi} multi-objective search-based test data generation

\cite{cao2009search} multi-path search-based test data generation

\cite{awedikian2009mc} MC/DC test input generation

\cite{shahbazi2016black} generation of string test data

\cite{fraser2012mutation} mutation-driven generation of unit tests and oracles

\cite{havrikov2014xmlmate} XMLMate: evolutionary XML test generation.

\cite{mcminn2004search} seminal survey of search-based test data generation techniques.

\cite{mcminn2011search} recent overview of search-based testing.

\cite{mairhofer2011search} search-based testing for dynamic languages (Ruby)

\cite{baars2011symbolic} combines dynamic analysis with symbolic information to improve search-based testing

\cite{alshahwan2011automated} automated web application testing using search based software techniques.

\cite{ma2015grt} guided random testing

\cite{mao2016sapienz} Multi-objective automated testing for Android application

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{icse2018.bib}
